Cloud-SAP: Self-adaptive platform for scaling users' application deployed in a federation of cloud computing environments

### 2013-09-16 article/article.tex
Added architecture section

\section{Architecture of SAP-Cloud}

@@

% Non-BibTeX users please use
\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
\bibitem{NIST}
  {Mell, P. and Grance, T.}, {The NIST Definition of Cloud Computing}, 2011
\bibitem{InterCloud}
  {Buyya, R. Ranjan, R. and Calheiros, R.}, {InterCloud: Scaling of Applications across multiple Cloud Computing Environments}, 2010
\bibitem{MarketOriented}
  {Buyyaa, R., Yeoa, C., Venugopala, S., d Broberga, J. and Brandicc, I.}, {Cloud computing and emerging IT platforms: Vision, hype, and reality for delivering computing as the 5th utility}, {Future Generation Computer Systems}, vol.25, 2009
\bibitem{ScalingInDaCloud}
  {Vaquero, L., Rodero-Merino, L. and Buyya, R.}, {Dynamically Scaling Applications in the Cloud}, {ACM SIGCOMM Computer Communication Review}, vol.41, 2011
\bibitem{ScalabilityTerm}
  Bondi, A., {Characteristics of Scalability and Their Impact on Performance}, 2000
\bibitem{PharmaComputation}
  Jon Brodkin, \emph{\$1,279-per-hour, 30,000-core cluster built on Amazon EC2 cloud}, {\emph{Ars Technica}, \url{http://arstechnica.com/business/2011/09/30000-core-cluster-built-on-amazon-ec2-cloud/}}, last access: 16/09/2013
\bibitem{AWS}
  {Amazon Elastic Compute Cloud (EC2)}, {\url{http://aws.amazon.com/}}, last access: 16/09/2013 
\bibitem{GoogleAppEngine}
  {Google App Engine}, {\url{https://appengine.google.com/}}, last access: 16/09/2013 
\bibitem{Heroku}
  {Heroku}, {\url{https://www.heroku.com}}, last access: 16/09/2013 
\bibitem{Azure}
  {Windows Azure}, {\url{www.windowsazure.com/}}, last access: 16/09/2013 
\bibitem{VaRoBu11}
  {Vaquero, L., Rodero-Merino, L. and Buyya, R.},{Dynamically Scaling Applications in the Cloud}, {ACM SIGCOMM Computer Communication Review}, vol.41, 2011
\bibitem{LiWoZh05}
 {Litoiu, M. and Woodside, M. and Zheng, T.}, {Hierarchical Model-based Autonomic Control of Software Systems}, {Design and evolution of autonomic application software}, 2005

>>>>

\section{Architecture of Cloud-SAP}

One can notice that elements that yields a solution for a problem stated at the begging of this article, which is ensuring that users' application provide appropriate Quality-of-Service for its customers, were introduced in previous sections:
\begin{itemize}
	\item scalability - ability to improve application performance by enriching 
	\item adaptivity - ability to adapt (i.e. scale) appropriately to current usage pattern
	\item inter-cloud awareness - ability to cooperate with different cloud provider to supply application with extra resources
\end{itemize}

To begin with, different scalability models were introduced. Noticeably, they operated at different layers: 
\begin{itemize}
	\item application platform tuning
	\item single-server level (vertical scaling)
	\item multi-server level (horizontal scaling) 
	\item inter-cloud level (scaling out across different cloud-providers, concept introduced in previous chapter)
\end{itemize}
Consequently, it is expected that proposed solution's architecture reflects that multi-layered model, which hasn't been yet introduced to the marked. Additionally, each layer has to be characterized by an ability to adapt to a given application usage. As previous chapter stated, this can be achieved by adding a elasticity controller to each layer. This observation is a foundation of proposed architecture.

One of the first models that ensured system adaptivity is an autonomic component, concept based on a feed-back loop, initially proposed by IBM \cite{IBM06}. Figure \ref{ch5:autonomic-component} depicts that architecture.

\begin{figure}[!ht]
  \includegraphics[width=0.47\textwidth]{drawings/autonomic-component}
  \caption{Autonomic component}
  \label{ch5:autonomic-component}
\end{figure}

Since designed platform operates on multiple layers, we can extend that model by using concept of a multi-hierarchical autonomic system \cite{LiWoZh05}. Figure \ref{ch5:hierarchical-autonomic-system} illustrates that hierarchy, were each level represents a different perspective at application scaling. Using terminology characteristic to a autonomic system, first three hierarchy levels (application tuning, single-server, multi-server) are centralized and controlled by single elasticity controller at each level, while the last inter-cloud level is a decentralized one - each cloud instance is fully independent.

\begin{figure*}[!ht]
  \includegraphics{drawings/hierarchical-autonomic-system}
  \caption{Hierarchical autonomic system}
  \label{ch5:hierarchical-autonomic-system}
\end{figure*}

As \cite{IBM06} states, each autonomic component has modules that are responsible for:
\begin{itemize}
	\item monitoring
	\item analysis
	\item planning
	\item action execution
\end{itemize}

While the managed component has:
\begin{itemize}
	\item sensors
	\item effectors
\end{itemize}

Due to the hierarchy of our architecture, each level manages an underlying autonomic component, while being managed by an upper layer at the same time. This lead us to observation that they are autonomic components and managed components at the same time.

@@

% Non-BibTeX users please use
\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
\bibitem{NIST}
  {Mell, P. and Grance, T.}, {The NIST Definition of Cloud Computing}, 2011
\bibitem{InterCloud}
  {Buyya, R. Ranjan, R. and Calheiros, R.}, {InterCloud: Scaling of Applications across multiple Cloud Computing Environments}, 2010
\bibitem{MarketOriented}
  {Buyyaa, R., Yeoa, C., Venugopala, S., d Broberga, J. and Brandicc, I.}, {Cloud computing and emerging IT platforms: Vision, hype, and reality for delivering computing as the 5th utility}, {Future Generation Computer Systems}, vol.25, 2009
\bibitem{ScalingInDaCloud}
  {Vaquero, L., Rodero-Merino, L. and Buyya, R.}, {Dynamically Scaling Applications in the Cloud}, {ACM SIGCOMM Computer Communication Review}, vol.41, 2011
\bibitem{ScalabilityTerm}
  Bondi, A., {Characteristics of Scalability and Their Impact on Performance}, 2000
\bibitem{PharmaComputation}
  Jon Brodkin, \emph{\$1,279-per-hour, 30,000-core cluster built on Amazon EC2 cloud}, {\emph{Ars Technica}, \url{http://arstechnica.com/business/2011/09/30000-core-cluster-built-on-amazon-ec2-cloud/}}, last access: 16/09/2013
\bibitem{AWS}
  {Amazon Elastic Compute Cloud (EC2)}, {\url{http://aws.amazon.com/}}, last access: 16/09/2013 
\bibitem{GoogleAppEngine}
  {Google App Engine}, {\url{https://appengine.google.com/}}, last access: 16/09/2013 
\bibitem{Heroku}
  {Heroku}, {\url{https://www.heroku.com}}, last access: 16/09/2013 
\bibitem{Azure}
  {Windows Azure}, {\url{www.windowsazure.com/}}, last access: 16/09/2013 
\bibitem{VaRoBu11}
  {Vaquero, L., Rodero-Merino, L. and Buyya, R.},{Dynamically Scaling Applications in the Cloud}, {ACM SIGCOMM Computer Communication Review}, vol.41, 2011
\bibitem{LiWoZh05}
 {Litoiu, M. and Woodside, M. and Zheng, T.}, {Hierarchical Model-based Autonomic Control of Software Systems}, {Design and evolution of autonomic application software}, 2005
\bibitem{IBM06}
 {IBM}, {An architectural blueprint for autonomic computing, 4th edition}, 2006
